SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-31 2017-Xudong-SMT/ActaInformatica.tex
Correct some typos in proof of Th.2
AO seems the wrong typing of OA, as the result is OA in line 12 of Alg.
a little more

\begin{algorithm}[h]
  \caption{Open Automaton Generation}
  \label{alg1}
\begin{algorithmic}[1]
\Require A pNet $P$ (can be a PLTS, but not a hole)
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
\While{!$\mathit{isEmpty}(U)$}
	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
	\For {each $\mathit{OT} \in \mathit{OTs}$}
          \State Add $\mathit{OT}$ to $L$;
          \State Let $S'$ be the target state of $\mathit{OT}$
          Add $S'$ to the unexplored states if necessary:
	  \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
	  \EndFor
\EndWhile
\State $\mathit{L1}$=filterUnsatTransitions($\mathit{L,Assignments}$);
\State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$;
\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{AO_{n-1}}$)
\Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$; \Comment Fixpoint reached
\State \Return $\mathit{OA_n}$;

@@

\begin{algorithm}[h]
  \caption{``Smart'' Reachable Open Automaton Generation}
  \label{alg3}
\begin{algorithmic}[1]
\Require A pNet $P$ (cannot be a hole)
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
\While{!$\mathit{isEmpty}(U)$}
	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
	\For {each $\mathit{OT} \in \mathit{OTs}$}
        Check satisfiability of $\mathit{OT}$ using the SMT solver;
        \IfThen {$SAT(\mathit{OT})$}
                {\State \{Add $\mathit{OT}$ to $L$;
                  \State Let $S'$ be the target global state of $\mathit{OT}$
	          \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
                  \}}
	\EndFor
\EndWhile
\State $\mathit{L2}$=filterUnsatTransitions($\mathit{L,Assignments}$);
\State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L2)$;
\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{AO_{n-1}}$)
\Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$;
\State \Return $\mathit{OA_n}$;
%\EndIf
\end{algorithmic}  
\end{algorithm}

@@

  Let us first define some notations.
 \begin{itemize}
    \item $L0$: the original set of transitions by Algorithm 1
      (i.e. before line 11), 
    \item $L1_{sat}$:  the original set of transitions by Algorithm 1, after
      satisfiability check (i.e. after line 11),
    \item $L1_{reach}$: the final set of OTs of Algorithm 1, as computed
      by line 12 (as $AO_0$). Without assignments the following
      refinement step will do nothing, the fixpoint is already reached.
    \item $L2_{sat}$: the original set of transitions by Algorithm 3
      (i.e. before line 13), 
    \item $L2_{reach}$: the final set of OTs of Algorithm 2, as computed
          by line 13. Here also $AO_n = AO_0$.
\end{itemize}

@@

\medskip
We will prove by induction on the distance from the original state,
that $\forall S \in L0. \forall n \in \mathbb{N}. S \in States(L2_{reach}) \land |S|_{l2_{reach}}=n => S
\in States(L1_{reach})$, and vice-versa.

@@

  Suppose our property is true for distance $n$, and
  suppose $|S|_{L2_{reach}}=n+1$, then there exist a chain
  $S_0\xrightarrow{l_1}S_1\xrightarrow{l_2}...S_{n}\xrightarrow{l_{n+1}}S$
  with all $l_k \in L2_{reach}$. In particular, as
  $L2_{reach}\subseteq L2_{sat}$, $l_{n+1} \in L2_{sat}$, meaning 
  it's predicate is satisfiable.

>>>>

\begin{algorithm}[h]
  \caption{Open Automaton Generation}
  \label{alg1}
\begin{algorithmic}[1]
\Require A pNet $P$ (can be a PLTS, but not a hole)
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
\While{!$\mathit{isEmpty}(U)$}
	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
	\For {each $\mathit{OT} \in \mathit{OTs}$}
          \State Add $\mathit{OT}$ to $L$;
          \State Let $S'$ be the target state of $\mathit{OT}$
          Add $S'$ to the unexplored states if necessary:
	  \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
	  \EndFor
\EndWhile
\State $\mathit{L1}$=filterUnsatTransitions($\mathit{L,Assignments}$);
\State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$;
\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{OA_{n-1}}$)
\Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$; \Comment Fixpoint reached
\State \Return $\mathit{OA_n}$;

@@

\begin{algorithm}[h]
  \caption{``Smart'' Reachable Open Automaton Generation}
  \label{alg3}
\begin{algorithmic}[1]
\Require A pNet $P$ (cannot be a hole)
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
\While{!$\mathit{isEmpty}(U)$}
	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
	\For {each $\mathit{OT} \in \mathit{OTs}$}
        Check satisfiability of $\mathit{OT}$ using the SMT solver;
        \IfThen {$SAT(\mathit{OT})$}
                {\State \{Add $\mathit{OT}$ to $L$;
                  \State Let $S'$ be the target global state of $\mathit{OT}$
	          \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
                  \}}
	\EndFor
\EndWhile
\State $\mathit{L2}$=filterUnsatTransitions($\mathit{L,Assignments}$);
\State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L2)$;
\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{OA_{n-1}}$)
\Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$;
\State \Return $\mathit{OA_n}$;
%\EndIf
\end{algorithmic}  
\end{algorithm}

@@

  Let us first define some notations.
 \begin{itemize}
    \item $L0$: the original set of transitions by Algorithm 1
      (i.e. before line 11), 
    \item $L1_{sat}$:  the original set of transitions by Algorithm 1, after
      satisfiability check (i.e. after line 11),
    \item $L1_{reach}$: the final set of OTs of Algorithm 1, as computed
      by line 12 (as $OA_0$). Without assignments the following
      refinement step will do nothing, the fixpoint is already reached.
    \item $L2_{sat}$: the original set of transitions by Algorithm 3
      (i.e. before line 13), 
    \item $L2_{reach}$: the final set of OTs of Algorithm 2, as computed
          by line 13. Here also $OA_n = OA_0$.
\end{itemize}

@@

\medskip
We will prove by induction on the distance from the original state,
that $\forall S \in L0. \forall n \in \mathbb{N}. S \in States(L2_{reach}) \land |S|_{L2_{reach}}=n \Rightarrow S
\in States(L1_{reach})$, and vice-versa.

@@

  Suppose our property is true for distance $n$, and
  suppose $|S|_{L2_{reach}}=n+1$, then there exists a chain
  $S_0\xrightarrow{l_1}S_1\xrightarrow{l_2}...S_{n}\xrightarrow{l_{n+1}}S$
  with all $l_k \in L2_{reach}$. In particular, as
  $L2_{reach}\subseteq L2_{sat}$, $l_{n+1} \in L2_{sat}$, meaning 
  its predicate is satisfiable.
